|

### 2019-12-31 docs/manuscript.Rmd
fixing title

---
title: |
 and potential for expanded access to prevent human rabies deaths in Madagascar
 How accesss to care shapes disease burden: the current impact of post-exposure prophylaxis 
author:
  - Malavika Rajeev:
      email: mrajeev@princeton.edu
      institute: [Princeton]
      correspondence: true
  - Helene Guis:
      institute: [IPMepi, CIRAD]
      correspondence: false
  - Glenn Edosoa:
      institute: [OMS]
      correspondence: false
  - Chantal Hanitriniaina:
      institute: [UoA]
      correspondence: false
  - Soa Fy Andriamandimby:
      institute: [IPMviro]
      correspondence: false
  - Anjasoa:
      institute: [IPMepi]
      correspondence: false
  - Reziky:
      institute: [IPMepi]
      correspondence: false
  - Ravo:
      institute: [IPMvacc]
      correspondence: false
  - Laurence Baril:
      institute: [IC]
      correspondence: false
  - C.J.E. Metcalf:
      institute: [Princeton]
      correspondence: false
  - Katie Hampson:
      institute: [Glasgow]
      correspondence: false
institute:
  - Princeton: Department of Ecology and Evolutionary Biology, Princeton University, Princeton, United States
  - IPMviro: Virology Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMvacc: Vaccination Center, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMepi: Epidemiology and Clinical Research Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IC: Institut Pasteur de Cambodge
  - CIRAD: CIRAD, UMR ASTRE, Antananarivo, Madagascar
  - OMS: OMS
  - UoA: Mention Zoologie et Biodiversité Animale, Faculté des Sciences, Université d’Antananarivo, Antananarivo, Madagascar
  - Glasgow: Boyd Orr Centre for Population and Ecosystem Health, Institute of Biodiversity, Animal Health and Comparative Medicine, University of Glasgow, Glasgow, UK
date: ""
link-citations: no
output:
 bookdown::word_document2:
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --filter=pandoc-crossref
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
      - --reference-doc=format/Reference_Document.docx
 bookdown::gitbook:
    toc: true
    toc_float: true
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --filter=pandoc-crossref
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
keywords: "canine rabies, post-exposure prophylaxis, Gavi, Zero by 30, access to care"
bibliography: ["bib/refs_all.bib"]
---

>>>>

---
title: |
 How accesss to care shapes disease burden: the current impact of post-exposure prophylaxis 
 and potential for expanded access to prevent human rabies deaths in Madagascar
author:
  - Malavika Rajeev:
      email: mrajeev@princeton.edu
      institute: [Princeton]
      correspondence: true
  - Helene Guis:
      institute: [IPMepi, CIRAD]
      correspondence: false
  - Glenn Edosoa:
      institute: [OMS]
      correspondence: false
  - Chantal Hanitriniaina:
      institute: [UoA]
      correspondence: false
  - Soa Fy Andriamandimby:
      institute: [IPMviro]
      correspondence: false
  - Anjasoa:
      institute: [IPMepi]
      correspondence: false
  - Reziky:
      institute: [IPMepi]
      correspondence: false
  - Ravo:
      institute: [IPMvacc]
      correspondence: false
  - Laurence Baril:
      institute: [IC]
      correspondence: false
  - C.J.E. Metcalf:
      institute: [Princeton]
      correspondence: false
  - Katie Hampson:
      institute: [Glasgow]
      correspondence: false
institute:
  - Princeton: Department of Ecology and Evolutionary Biology, Princeton University, Princeton, United States
  - IPMviro: Virology Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMvacc: Vaccination Center, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IPMepi: Epidemiology and Clinical Research Unit, Institut Pasteur de Madagascar, Antananarivo, Madagascar
  - IC: Institut Pasteur de Cambodge
  - CIRAD: CIRAD, UMR ASTRE, Antananarivo, Madagascar
  - OMS: OMS
  - UoA: Mention Zoologie et Biodiversité Animale, Faculté des Sciences, Université d’Antananarivo, Antananarivo, Madagascar
  - Glasgow: Boyd Orr Centre for Population and Ecosystem Health, Institute of Biodiversity, Animal Health and Comparative Medicine, University of Glasgow, Glasgow, UK
date: ""
link-citations: no
output:
 bookdown::word_document2:
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --filter=pandoc-crossref
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
      - --reference-doc=format/Reference_Document.docx
 bookdown::gitbook:
    toc: true
    toc_float: true
    pandoc_args:
      - --csl=format/plos-neglected-tropical-diseases.csl
      - --filter=pandoc-crossref
      - --lua-filter=format/scholarly-metadata.lua
      - --lua-filter=format/author-info-blocks.lua
      - --lua-filter=format/pagebreak.lua
      - --lua-filter=format/multiple-bibliographies.lua
keywords: "canine rabies, post-exposure prophylaxis, Gavi, Zero by 30, access to care"
bibliography: ["bib/refs_all.bib"]
---
